A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2018-06-27 manuscript/coverletter.tex
spellchecked

    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of emprical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}. The goals of this manuscript are A) to illustrate the extreme difficulty in fully sampling the set of interactions occurring within a community, B) to demonstrate the construction of networks treating each interaction probabilistically (based on prior information as well as available data), and C) to offer concrete recommendations that will facilitate the use of this framework in future work.

    We argue that, because of multiple levels of uncertainty surrounding interactions between species, the set of observed interactions will almost certainly be a subset of the interactions that can occur in a community. Some interactions may be rare because of species traits (e.g., prey that are only consumed by the largest individuals of a predator species), others may be difficult to detect because they occur under conditions not conducive to sampling (e.g., during inclement weather or at night), and yet other interactions may be common but very difficult to detect (e.g., interactions involving species that are highly cryptic). We emphasize that some of these sources of uncertainty can be reduced with increased sampling but that, because it is easier to observe species than interactions between species, increased sampling will tend to add more unobserved than observed interactions to a matrix. We illustrate the problem using an extensively-sampled, spatially-replicated \emph{Salix}-galler-natural enemy system (Kopelke \emph{et al.}, 2017. \textbf{Ecology} 98: 1730).

>>>>

    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}. The goals of this manuscript are A) to illustrate the extreme difficulty in fully sampling the set of interactions occurring within a community, B) to demonstrate the construction of networks treating each interaction probabilistically (based on prior information as well as available data), and C) to offer concrete recommendations that will facilitate the use of this framework in future work.

    We argue that, because of multiple levels of uncertainty surrounding interactions between species, the set of observed interactions will almost certainly be a subset of the interactions that can occur in a community. Some interactions may be rare because of species traits (e.g., prey that are only consumed by the largest individuals of a predator species), others may be difficult to detect because they occur under conditions not conducive to sampling (e.g., during inclement weather or at night), and yet other interactions may be common but very difficult to detect (e.g., interactions involving species that are highly cryptic). We emphasise that some of these sources of uncertainty can be reduced with increased sampling but that, because it is easier to observe species than interactions between species, increased sampling will tend to add more unobserved than observed interactions to a matrix. We illustrate the problem using an extensively-sampled, spatially-replicated \emph{Salix}-galler-natural enemy system (Kopelke \emph{et al.}, 2017. \textbf{Ecology} 98: 1730).
